\title{COMP 354: Diary - Iteration 2}
\author{
        Anne-Laure Ehresmann \\
        ID: 27858906}
\date{\today}
\setlength{\parindent}{0pt}
\documentclass[12pt]{article}
\begin{document}
\maketitle

\subsection*{March 4, 12:30-4:00 pm 2018}
I, Keith, Abed and Hrachya met up for a coding session where we went over the project structure. We discussed the tasks assigned to the coders and did some coding.

\subsection*{March 4, 2018}
Minor change to the build file to solve the building issues on Linux platform.

\subsection*{March 5, 2018}
Created deleteAccount function and the tests. Did minor modifications to the TestUtils class.

\subsection*{March 6, 1:30-2:00 pm 2018}
Went over the existing architecture and did modifications with Hrachya. Discussed the test cases required for deleteBankAccount.

\subsection*{March 7,  2018}
Changed passing account in deleteAccount() in accountService to pass the account ID. Modified appropriate tests. \\
Created appropriate authentication and authorisation excpetions and made sure to test for them. \\
Added tests for deleteBankAccount() in UserService. \\
Finished deleteBankAccount() in UserService. 

\subsection*{March 12,  2018}
 Added the delete account functionality to the AccountListController. Performed manual GUI testing.
 
 \subsection*{March 13,  2018}
Added business rules, corrections to the design document. \\
Large Modifications to the introduction and the scope of the design document. \\
Organisational changes to the documentation folder.

\subsection*{March 13, 1:00-2:00 pm 2018}
Meeting with Abed and Keith. Went over tests we had in common for our task and solved some bugs in Keith's code. Abed left to his class.

\subsection*{March 13, 2:00-4:00 pm 2018}
Continued meeting with Keith where we tried to implement his update user controller. Had some problems with FXML and database update integration, Hrachya came to help at 2:30 and left at 3:00.

 \subsection*{March 14,  2018}
Added business rules, minor corrections to the design document. \\
Modifications to the introduction and the architectural design of the design document. \\
Organisational changes to the documentation folder.

 \subsection*{March 17,  2018}
Major changes to the design document: modified the architecture diagram to include view controllers. \\ Changed paragraph structure. \\
Modified account details and account list sequence diagrams.

 \subsection*{March 18,  2018. 15:00 00:00}
Meeting with Hrachya. Went over the design document, large changes done. \\
Added missing view controller class descriptions. \\
Renamed several packages. \\
Changes to the Architecture description and subsystem design specifications. \\
submitted documentation.
\end{document}