\title{COMP 354: Diary - Iteration 1}
\author{
        Anne-Laure Ehresmann \\
        ID: 27858906}
\date{\today}
\setlength{\parindent}{0pt}
\documentclass[12pt]{article}
\begin{document}
\maketitle

\subsection*{Jan. 22 - 28}

\begin{itemize}
    \item Began requirements document, provided a tex template for use-case, and wrote use case 1.
\end{itemize}

Overall, in the first week I put about 2 hours of  work on the project, outside of our meetings. That week we mostly got to know each other, convened on who would do what, and tried to agree on a coherent, structured plan for our project.

\subsection*{Jan. 29 - Feb. 4}

\begin{itemize}
    \item met with Hrachya on wednesday 7th, convened on code and documentation consistency.
    \item Wrote use case 1-4
    \item Minor edits in use-cases 5-7
    \item SQL diagram
    \item Use-case diagram
    \item Finalised use-cases 1, 3, 5, and 6 for iteration 1.
    \item Wrote requirements purpose and business goals
    \item Wrote description of actors
    \item Wrote majority of non-functional requirements, most of which were done with Hrachya
\end{itemize}

Overall,  in the second week I put about 10 hours of work on the project, outside of our meetings. This is where the documenters started getting a clearer idea on what to do. Hrachya took charge of the programming side of the project during the first few meetings, especially since Marc got ill, we needed a replacement programmer. Hrachya and I we convened to try and keep both sides of the group on the same track. 


\subsection*{Feb. 5 - Feb. 11}
\begin{itemize}
    \item Wrote introduction, System Context, Scope, description of Business Goals, introduction to domain model, introduction to class diagram
    \item many edits to wording, spelling mistakes, formatting
    \item did latex environment for non-functional requirements
    \item added many terms to glossary
    \item wrote description of file formats
    \item wrote reference
    \item met with Hrachya on Wednesday 7th and Thursday the 8th, rewrote many non-functional requirements, organised document more properly, more wording edits.
\end{itemize}

Overall,in the last week I put about 15 hours of work on the project, outside of our meetings. I would say we definitely suffered from a lack of last minute organisation here. A bulk of the outside work was put during the last few days, I really felt like there was a lot to add to make our document presentable. Quality control helped us to make sure we didn't have formatting and spelling mistakes. A lot of my time was also spent just making sure we were meeting the expectations, so a lot of rereading the given documentation.

\end{document}