\title{COMP 354: Diary}
\author{
        DUBE Marc-Antoine \\
        40029307
}
\date{\today}
\setlength{\parindent}{0pt}
\documentclass[12pt]{article}
\begin{document}
\maketitle

\section{Iteration 1: Coder}
As a coder, I had to develop the core of the application and then focus on my use case.

\subsection{Week 1}
Nothing done that week as the project had not been started and we had not met our teams.

\subsection{Week 2}
Week 2 was the beginning of the project.

\subsubsection{Team Meeting}
\begin{itemize}
    \item First team meeting
    \item Discuss the project
    \item Split the team in different groups
    \item Discuss the technologies to be used in the project
\end{itemize}

\subsubsection{Tasks performed}
\item Create the foundations for the code
\begin{itemize}
    \item Configure Gradle as our build and dependency manager
    \item Configure Dagger as our dependency injection framework
    \item Configure JavaFX as our front-end technology
\end{itemize}

\subsection{Week 3}
In week 3, we mainly discussed our use cases and domain models during the lab.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Work on the domain model as a team
    \item Work on the use case diagrams as a team
    \item Present the code foundations to the other coders and other interested members of the team
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Start writing basic services and DAOs
\end{itemize}

\subsection{Week 4}
The end of week 3 and week 4 were tough.
I had an appendicitis that required surgery and I could not work to my full potential.
I missed the lab on Wednesday.
I missed the lecture and the tutorial on Thursday.

\subsection{Week 5}
Week 5 was mostly a week to complete the first iteration and make sure that everything was done properly.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Verify if everything is done in each part of the iteration
    \item Distribute new roles for the next iteration
    \item Discuss tasks for the next iteration
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Connect the login and signup front-end to the back-end
    \item Connect the transactions front-end to the back-end
    \item Refactor views to avoid code duplication
\end{itemize}

\subsection{Commits}
\begin{itemize}
    \item Jan 18, 2018
        \subitem [FEAT] Create basic application with JavaFX and Gradle
    \item Jan 19, 2018
        \subitem [FEAT] Add Dagger auto injection configuration and basic class example
    \item Commits on Jan 25, 2018
        \subitem [FEAT] Add user service/dao
        \subitem [DOC] Add documentation to where Dagger is used
    \item Jan 30, 2018
        \subitem [DOC] Add personal diary
    \item Feb 1, 2018
        \subitem [DOC] Add name to requirements document
    \item Feb 6, 2018
        \subitem [FEAT] Add session manager and show login errors
    \item Feb 7, 2018
        \subitem [FIX] Remove delete account button for next iteration
        \subitem [FEAT] Connect signup front end and backend
        \subitem [BUILD] Add data to setup.sql script
        \subitem [FEAT] Connect addAccount front end to backend and add AlertHelper class to display validation errors
        \subitem [REFACTOR] Revert SessionManager interface creation
        \subitem [FIX] Fix SessionManager not instantiated as singleton
    \item Feb 9, 2018
        \subitem [REFACTOR] Create TransactionTable view to avoid repeating code
        \subitem [REFACTOR] Separate all transactions view from account display view
\end{itemize}


\section{Iteration 2: Organiser}
As an organiser, I made sure that the tasks were on time.
I also took care of setting up meetings. I also helped the documenters and the coders when needed.

\subsection{Week 6}
Week 6 was a transition week.
We transitioned into our new roles by presenting the code to the new coders and documenters doing the same thing with their documents for the new documenters.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Coders from iteration 1 explain the code to the new coders for iteration 2 (and to others if interested)
    \item Documenters from iteration 1 show the documents created in iteration 1
    \item Coders separate the use cases and other tasks to be coded
    \item Documenters separate the content to be written (Architectural and detailed design specification)
    \item Discuss what worked well and less well in the first iteration
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Prepare the meeting for week 6
    \item Distribute the tasks between everyone and note them in Github
\end{itemize}

\subsection{Week 6.5 (Reading week)}
This week was reading week.

\subsubsection{Team Meeting}
No team meeting

\subsubsection{Tasks performed}
\begin{itemize}
    \item Configure Travis CI to have a Continuous Integration platform to build our project on
\end{itemize}

\subsection{Week 7}
In week 7, the team studied the tasks that were to be done.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Discuss what was done in the last 2 weeks. What is there left to do?
    \item Documenters should discuss the sequence diagrams and how they will be made. 1 could be done as a team during the lab.
    \item Coders should ask questions about the codebase if there is something they need to be explained.
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Prepare the meeting for week 7
\end{itemize}

\subsection{Week 8}
Week 8 was demo week. As a team, we wanted to have about 75\% to 80\% of the work done to present the new features and the Design Document.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Documenters split the work for the description of the classes
    \item Documenters review the sequence diagrams
    \item Continue work on the use cases
    \item Code reviews
    \item Demo
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Prepare the meeting for week 8
    \item Write the Architectural Design section in the Design Document
    \item Add package diagram
    \item Explanation of the MVC
    \item Add subsystem interface diagram for the SignUpController
    \item Check where everyone is at with their tasks
\end{itemize}

\subsection{Week 9}
Week 9 was the final week of iteration 2, thus my final week as organiser.
We needed to complete the remaining tasks.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Coders complete tasks/refactoring, making sure there is no outstanding issue
    \item Code review
    \item Documenters discuss the class description tables and split the work
    \item Documenters double check everything is done/is going to be done before Saturday
    \item Discuss the submission and make sure everything is going to be done by the end of Saturday to have enough time to review.
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Prepare the meeting for week 9
    \item Help coders creating config functions for a table view
    \item Add class documentation in the Design Document
    \item Maintain the tasks log
\end{itemize}

\subsection{Commits}
\begin{itemize}
    \item Feb 13, 2018
        \subitem [DOC] Add week 06 meeting schedule
    \item Feb 14, 2018
        \subitem [DOC] Add tasks and assignees for iteration 2
    \item Feb 22, 2018
        \subitem [BUILD] Add basic Travis CI integration for builds/tests
    \item Feb 26, 2018
        \subitem [BUILD] Add Travis-CI build icon to README
        \subitem Create week07.md
    \item Mar 6, 2018
        \subitem Create week08.md
        \subitem [DOC] Start Architectural Design in the Design Document
    \item Mar 7, 2018
        \subitem [DOC] Update tasks for documenters
        \subitem Update iteration02\_tasks.md
    \item Mar 11, 2018
        \subitem [DOC] Update package diagrams
        \subitem [DOC] Add detailed diagram module/dagger explanation
        \subitem [DOC] Add SignUpController subsystem interface diagram
    \item Mar 13, 2018
        \subitem Add week 09 lab meeting
        \subitem Update iteration02\_tasks.md
        \subitem Update if the tasks are done or not
    \item Mar 14, 2018
        \subitem [DOC] Edit class table template
        \subitem [FEAT] Add column ID to TransactionTableController
        \subitem [REVERT] Revert previous commit
    \item Mar 16, 2018
        \subitem [DOC] Add com.github.comp354project class descriptions
        \subitem [DOC] Add com.github.comp354project.service.dao class descriptions
        \subitem [DOC] Add missing captions to tables and fix some properties
        \subitem [DOC] Add class documentation for sqlite package
        \subitem [DOC] Update design document PDF
        \subitem [DOC] Update tasks
    \item Mar 17, 2018
        \subitem [DOC] Add dependencies to subsystem interface diagram of AccountListController
        \subitem [DOC] Reformat some tables
    \item Mar 18, 2018
        \subitem [DOC] Add model.auth package class description
        \subitem [DOC] Add exceptions class description
        \subitem [DOC] Add DI terms to glossary
        \subitem [DOC] Add MVC diagram
\end{itemize}

\section{Iteration 3: Documenter}
As a documenter, I worked on the test document.
Most of the tables that needed to be written were very similar, so I wrote scripts to parse the table information formatted in JSON. That way, it was easier to keep consistent looks and do modifications between everyone's work.

\subsection{Week 10}
Week 10 was the first week of the final iteration.
Not much work was done because people studied for the quiz.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Choose new roles for the iteration
    \item Separate the tasks to be done and use cases to be implemented
    \item Find the best strategy on how to implement the use cases
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Create the issues in a Github project board to keep track of the statuses of the tasks
\end{itemize}

\subsection{Week 11}
I mainly worked on creating a script in javascript to generate our Latex tables from JSON.

\subsubsection{Team Meeting}

We were only 4 present at the meeting.

\begin{itemize}
    \item Show the progress done in each task
    \item Study for the quiz
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Format the template for the test document
    \item Create script to generate unit test documentation tables
    \item Write the unit test descriptions for all the test cases
\end{itemize}

\subsection{Week 12}
Week 12 was demo week before handing in the project on Sunday.
We presented the demo and asked many questions on how to write sections of the test document.

\subsubsection{Team Meeting}
\begin{itemize}
    \item Present our work for the demo
    \item Ask questions on functional vs acceptance and performance testing
    \item Keep track on where everyone is at for their tasks
\end{itemize}

\subsubsection{Tasks performed}
\begin{itemize}
    \item Write functional tests
    \item Write glossary items
    \item Fix failing build due to code compilation error
\end{itemize}

\subsection{Commits}
\begin{itemize}
    \item Mar 28, 2018
        \subitem [DOC] Add test table template
    \item Mar 30, 2018
        \subitem [DOC] Add json test definitions for UserService.createUser
    \item Mar 31, 2018
        \subitem  [FEAT] Start test table generator
        \subitem  [FEAT] Complete test table script generator templating
    \item Apr 1, 2018
        \subitem [FIX] Fix hardcoded cline in test table generator
        \subitem [FEAT] Read argument from command line
        \subitem [DOC] Add delete bank account test doc
        \subitem [DOC] Add delete bank account test doc latex and pdf
        \subitem [DOC] Add delete account and update user test documentation
        \subitem [DOC] Add login and logout session manager test doc
    \item Apr 3, 2018
        \subitem [DOC] Add remote account service test doc
    \item Apr 5, 2018
        \subitem [FIX] Add missing .java extension to SendMailController
        \subitem [FIX] Compile errors in TransactionGenerateFileController
        \subitem [REFACTOR] Append timestamp to generated csv file
    \item Apr 6, 2018
        \subitem [DOC] Add use case 11 functional testing
        \subitem [DOC] Add use case 12 functional testing
        \subitem [DOC] Add use case 13 functional testing
    \item Apr 8, 2018
        \subitem [DOC] Add glossary and glossary table scripts generator
        \subitem [DOC] Add func test 3 and 4 and generate the func test tex file
\end{itemize}

\end{document}